---
output:
  pdf_document: default
  html_document: default
---
Research Question: What is the relationship between users' tones and attitudes
towards gun control/campus gun violence related to their gender or resident state? 

Hypothesis 1: Females are more likely to have a negative sentiment towards campus gun violence.
Hypothesis 2: Users in blue states are more likely to have a negative sentiment towards campus gun violence.

### Data preparation and cleaning ###
Clean the Twitter data by removing special characters, URLs, digits and 
punctuation. Removing special characters is important at this stage, as these 
can interfere with many text parsers. Removing stopwords, on the other hand, is 
less important, as these typically have a neutral value in most sentiment analysis lexica.

```{r}
campus <-read.csv("/Users/ZXY/Desktop/A4/Group3new.csv", header=TRUE, sep=",") 
campus_text <-campus$Title
#Remove special characters, e.g., emoji
campus_text <- gsub("[^\x20-\x7e]"," ", campus_text) 
#Remove URLs, punctuation, and digits
campus_text <- gsub("(@|http)[^[:blank:]]*|[[:punct:]]|[[:digit:]]"," ", campus_text) 
#Remove extra spaces. perl=TRUE tells R to use the PCRE regular expressions library. 
campus_text <- gsub("(?<=[\\s])\\s*|^\\s+|\\s+$", "", campus_text, perl=TRUE) 

head(campus_text)
```

### Sentiment Analysis ###


```{r}
library(syuzhet)

sentiment_bing <- get_sentiment(campus_text, method = "bing")

sentiment_new<-ifelse(sentiment_bing < 0, -1, sentiment_bing) #Turn all negative sentiment values to -1
sentiment_new<-ifelse(sentiment_new > 0, 1, sentiment_new) #And turn all positive sentiment values to 1
sentiment_new<-ifelse(sentiment_new == 0, 0, sentiment_new) 

campus$sentiment<-sentiment_new #Add a column with the sentiment values to the dataframe

write.csv(campus, "/Users/ZXY/Desktop/A4/results.csv", row.names = FALSE)
```

### Hypothesis 1: Females are more likely to have a negative sentiment towards campus gun violence ###

```{r}
# Read the results from sentiment analysis
senti <-read.csv("/Users/ZXY/Desktop/A4/results.csv", header=TRUE, sep=",") 

# Convert every null value into "unknown"
for(i in 1:nrow(senti)){
  if(senti$Gender[i] == ""){
    senti$Gender[i] = "unknown"
  }
}

#Convert "female", "male", and "unknown" into 1, 2, and 3 and generate a new column
for(i in 1:nrow(senti)){
  if (senti$Gender[i] == "female") {
    campus$gender_number[i] = 1
  }
  if (senti$Gender[i] == "male") {
    campus$gender_number[i] = 2
  }
  if (senti$Gender[i] == "unknown") {
    campus$gender_number[i] = 3
  }
}
write.csv(campus, "/Users/ZXY/Desktop/A4/results.csv", row.names = FALSE)

# Calculate the average score for each gender ("female", "male", "unknown")
female_total_score = 0
female_count = 0
male_total_score = 0
male_count = 0
for (i in 1:nrow(senti)){
  if (senti$Gender[i] == "female"){
    female_total_score = female_total_score + senti$sentiment[i]
    female_count = female_count + 1
  }
  if (senti$Gender[i] == "male"){
    male_total_score = male_total_score + senti$sentiment[i]
    male_count = male_count + 1
  }
}

female_count
male_count
female_average_score <- female_total_score / female_count
male_average_score <- male_total_score / male_count

female_average_score
male_average_score
```
From the results, we can conclude that females are actually more likely to have 
negative sentiments towards campus gun violence.



### Hypothesis 2: Users in blue states are more likely to have a negative sentiment towards campus gun violence ###


```{r}
# Read the results from sentiment analysis
senti <-read.csv("/Users/ZXY/Desktop/A4/results.csv", header=TRUE, sep=",") 

blue_state <- list('AZ', 'CA', 'CO', 'CT', 'DE', 'GA', 'HI', 'IL', 'ME', 'MD', 
                   'MA', 'MI', 'MN', 'NV', 'NH', 'NJ', 'NM', 'NY', 'OR', 'PA', 
                   'RI', 'VT', 'VA', 'WA', 'WI')

red_state <- list('AL', 'AK', 'AR', 'FL', 'ID', 'IN', 'IA', 'KS', 'KY', 'LA',
                  'MS', 'MO', 'MT', 'NE', 'NC', 'ND', 'OH', 'OK', 'SC', 'SD',
                  'TN', 'UT', 'WV', 'WY')

# Calculate the average scores for "blue states" and "red states"
blue_state_total_score = 0
blue_state_count = 0
red_state_total_score = 0
red_state_count = 0
others = 0

for (i in 1:nrow(senti)){
  if (senti$City.Code[i] != ""){
    state <- toupper(substr(senti$City.Code[i], 5, 6))
    
    if (state %in% blue_state){
      blue_state_total_score = blue_state_total_score + senti$sentiment[i]
      blue_state_count = blue_state_count + 1
      senti$state_number[i] = 1
    } else if(state %in% red_state) {
      red_state_total_score = red_state_total_score + senti$sentiment[i]
      red_state_count = red_state_count + 1
      senti$state_number[i] = 2
    } else {
      others = others + 1
      senti$state_number[i] = 3
    }
  } else {
    senti$state_number[i] = 4
  }
}
write.csv(senti, "/Users/ZXY/Desktop/A4/results.csv", row.names = FALSE)
blue_state_average_score <- blue_state_total_score / blue_state_count
red_state_average_score <- red_state_total_score / red_state_count

blue_state_average_score
red_state_average_score
```
From the results, we can conclude that users in blue states are actually more likely to have 
negative sentiments towards campus gun violence.
